Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-05-25 paper_jasa.tex
definition of visual test

>>>>

\blue{To avoid confusion with one tailed $(1-\alpha)$ vs two tailed $(1-\alpha/2)$ notation, can we just use $x_{\alpha}$? }

\red{alternative definition of visual test where $type-I$ error $\alpha$ is attached.

\begin{dfn}\label{dfn:test}
The \textbf{visual test}, $V_{\theta}$  of size $\alpha$, is defined to be 
\begin{itemize}\itemsep-3pt
\item \textbf{Reject} $H_0$ if out of $K$ observers $x_{\alpha}$ of them correctly identify the observed data plot in the lineup, and
\item \textbf{Fail to reject} $H_0$  otherwise. %if the observer selects a null plot.
\end{itemize}
where $x_{\alpha}$ is such that $P(X \ge x_{\alpha}) < \alpha$. 
\end{dfn}

Notice that now we can fix $type-I$ error to some values even less than $1/m$ by increasing $K$. $type-I$ error is $1/m$ only when $K=1$.
}
